\LARGE \bf Artificial Cognition for Social Human-Robot Interaction:\\ An Implementation

### 2016-06-30 paper.tex
Proof-read Rachid's latest changes

The robot controller \cite{clodic2014key} (with the help of a task planner) decides what action to
execute next, and who should perform it, from the robot or the human (or both in
case of a collaborative action such as a handover \cite{Mainprice2012,waldhart2015planning}), how it should achieved and what signals should
be sensed and/or produced by the robot to facilitate human-robot joint action
\cite{sebanz2006joint,knoblich20113,pacherie2012phenomenology,vesper2010minimal}.
It finally controls and monitors its execution. The
operation continues until the goal is achieved, is declared unachievable or is
abandoned by the human~\cite{Klein2004}.

@@

We present first the main \emph{internal} cognitive capabilities, implemented in
the {\sc Oro} knowledge base itself, and then discuss successively the situation
assessment module {\sc Spark}, the dialogue processor {\sc Dialogs}, the
symbolic task planner HATP, and finally the main features of our execution
controllers {\sc Shary}\cite{clodic2008shary} and {\sc pyRobots}. Note that greater details on each of
these modules can be found in their respective publications (the corresponding
references are provided hereafter).

@@

{\sc Shary}'s originality, as an execution control system, lies in its ability
to take into account not only the task achievement but also the communication
and monitoring acts needed to support human-robot interactive task
achievement~\cite{Rich1997,Sidner2005,sebanz2006joint} in a flexible manner. {\sc Shary} allows
to bind action execution to \emph{communication policies} in order to produce
multi-modal signals towards the human and to react to human actions and signals. The
\emph{communication act} is the central concept in this formalism. It
represents an information exchange between the two agents and plays the role of
a transition condition. This exchange can be realised through speech, through an
expressive motion or a combination of the two. It enables each agent to
communicate their beliefs about the task to be achieved, in order to share
mutual knowledge and to synchronise their activities.  This is done through
real-time task-based situation assessment achieved by the combination of {\sc
Shary} monitoring processes and {\sc Oro} inference
mechanisms.

Two recent developments have been added that improve robot adaptation to human action at the action and at the plan level.  In~\cite{fiore2014}, the system is able to estimate its human intentions in collaborative tasks and to choose appropriate actions, using a set of POMDP models.  In~\cite{devin2016implemented}, a framework is proposed which allows the robot to estimate its human partner mental state not only about the environment but also about the state of goals, plans and actions and to take them into account when executing human-robot shared plans.

@@

The symbolic manipulation and navigation actions listed in
Table~\ref{table|pyrobots_actions} are eventually further refined and executed by the execution
controller with the help of a  set of dedicated human-aware geometric motion
planning functions provided by a component (called {\sc Mhp},
Figure~\ref{fig|archi}).

These functions are designed to plan navigation~\cite{Sisbot2007} and
manipulation~\cite{Mainprice2011,sisbot2012human} paths not only safe
but also comfortable and “socially acceptable” by reasoning explicitly
on human’s kinematics, vision field, posture and preferences
\cite{Madhava2006,kruse2013human,Rios-MartinezSL15}.  Besides, when necessary, they compute pertinent robot
and objects placements relative to the human\cite{Pandey2011}

Also, when an action needs motion of the human and the robot, it is
possible to plan for both of them in order to allow the robot to take
initiative by computing automatically where the interaction might
preferably take place\cite{Mainprice2012,waldhart2015planning}, 
thus decreasing the cognitive weight of interaction on human
side. This is somehow the geometric counterpart of HATP.

@@

We have presented in this paper a large deliberative architecture designed for
social robots. While most of its sub-components have been independently
presented in other publications, we offer here for the first time a perspective
on the model of integration of these components into a coherent and consistent
system for social human-robot interaction. We have first exposed our underlying
knowledge model based on Description Logics~\cite{Lemaignan2010} and some of the
resulting reasoning capabilities pertaining to disambiguation~\cite{Ros2010b}
and mental modelling~\cite{warnier2012when} that are shown to effectively
scaffold interaction using human-level semantics and cognitive skills. We have
then presented our approach to symbol grounding, build on an amodal situation
assessment environment~\cite{Sisbot2011} that supports perspective
taking~\cite{Marin2008,Ros2010}. We combine it further with a situated natural
language processor~\cite{Lemaignan2011a} to provide complete multi-modal
interactive communication.  The paper also covers our symbolic social task
planner~\cite{Alili2008, Alili2009, Lallement2014}: it generates predictive
plans of the human actions that enable the system to plan for joint human-robot
tasks. It can also make use of social heuristics to optimise plans for social
acceptability. We briefly mention our human-aware motion and manipulation
planner~\cite{Sisbot2008,Mainprice2011,Pandey2011}, and finally present two
execution controller, the PRS-based {\sc Shary}~\cite{clodic2008shary,fiore2014}
and the event-driven {\sc pyRobots}~\cite{lemaignan2015pyrobots}.

>>>>

The robot controller (with the help of a task planner) decides what action to
execute next~\cite{clodic2014key}, and who should perform it, from the robot or the human (or both in
case of a collaborative action such as a handover~\cite{Mainprice2012,waldhart2015planning}), how it should achieved and what signals should
be sensed and/or produced by the robot to facilitate human-robot joint action~\cite{sebanz2006joint,knoblich20113,pacherie2012phenomenology,vesper2010minimal}.
It finally controls and monitors its execution. The
operation continues until the goal is achieved, is declared unachievable or is
abandoned by the human~\cite{Klein2004}.

@@

We present first the main \emph{internal} cognitive capabilities, implemented in
the {\sc Oro} knowledge base itself, and then discuss successively the situation
assessment module {\sc Spark}, the dialogue processor {\sc Dialogs}, the
symbolic task planner HATP, and finally the main features of our execution
controllers {\sc Shary} and {\sc pyRobots}. Note that greater details on each of
these modules can be found in their respective publications (the corresponding
references are provided hereafter).

@@

Execution control systems for social robots are expected 
to account not only for the task achievement but also for the communication
and monitoring acts needed to support human-robot interactive task
achievement~\cite{Rich1997,Sidner2005,sebanz2006joint}. {\sc Shary} supports
such mechanisms. It allows
to bind action execution to \emph{communication policies} in order to produce
multi-modal signals towards the human and to react to human actions and signals. The
\emph{communication act} is the central concept in this formalism. It
represents an information exchange between the two agents and plays the role of
a transition condition. This exchange can be realised through speech, through an
expressive motion or a combination of the two. It enables each agent to
communicate their beliefs about the task to be achieved, in order to share
mutual knowledge and to synchronise their activities.  This is done through
real-time task-based situation assessment achieved by the combination of {\sc
Shary} monitoring processes and {\sc Oro} inference
mechanisms.

Two recent developments have further improved the robot's ability to adapt to
human action, both at the action level and at the plan level.
In~\cite{fiore2014}, an extension is proposed for the
system to estimate the intentions of the human during collaborative tasks using
POMDP models. The controller adjusts then appropriately the chosen set of actions.
In~\cite{devin2016implemented}, the controller is complemented with a framework
that allows the robot to estimate the mental state of the human partner, not
only related to the environment but also related to the state of goals, plans
and actions. They are then accounted for by the execution controller.

@@

The symbolic manipulation and navigation actions listed in
Table~\ref{table|pyrobots_actions} are eventually further refined and executed by the execution
controller with the help of a set of dedicated human-aware geometric motion
planning functions provided by a component called {\sc Mhp} (see Figure~\ref{fig|archi}).

These functions are designed to plan navigation~\cite{Sisbot2007} and
manipulation~\cite{Mainprice2011,sisbot2012human} paths not only safe but also
comfortable and socially acceptable by reasoning explicitly on human’s
kinematics, vision field, posture and
preferences~\cite{Madhava2006,kruse2013human,Rios-MartinezSL15}. They also
provide routines to compute spatial placements for robot and objects that obey
constraints related to the interaction, like optimal mutual reachability
or optimal visibility~\cite{Pandey2011}

Finally, when an action requires the motion of both the human and the robot,
{\sc Mhp} can plan for both of them in order for the robot to take
the lead by automatically computing where the interaction might
preferably take place~\cite{Mainprice2012,waldhart2015planning}.
This can effectively smoothen the interaction by off-loading a part of the
cognitive load of the interaction from the human to the robot.
As such, this is the geometric counterpart of the HATP symbolic task
planner.

@@

We have presented in this paper a large deliberative architecture designed for
social robots. While most of its sub-components have been independently
presented in other publications, we offer here for the first time a perspective
on the model of integration of these components into a coherent and consistent
system for social human-robot interaction. We have first exposed our underlying
knowledge model based on Description Logics~\cite{Lemaignan2010} and some of the
resulting reasoning capabilities pertaining to disambiguation~\cite{Ros2010b}
and mental modelling~\cite{warnier2012when} that are shown to effectively
scaffold interaction using human-level semantics and cognitive skills. We have
then presented our approach to symbol grounding, build on an amodal situation
assessment environment~\cite{Sisbot2011} that supports perspective
taking~\cite{Marin2008,Ros2010}. We combine it further with a situated natural
language processor~\cite{Lemaignan2011a} to provide complete multi-modal
interactive communication.  The paper also covers our symbolic social task
planner~\cite{Alili2008, Alili2009, Lallement2014}: it generates predictive
plans of the human actions that enable the system to plan for joint human-robot
tasks. It can also make use of social heuristics to optimise plans for social
acceptability. We briefly mention our human-aware motion and manipulation
planner~\cite{Sisbot2007,Sisbot2008,Mainprice2011,Pandey2011,sisbot2012human,kruse2013human}, and finally present two
execution controller, the PRS-based {\sc
Shary}~\cite{clodic2008shary,fiore2014,clodic2014key}
and the event-driven {\sc pyRobots}~\cite{lemaignan2015pyrobots}.
